### 2024-05-10 README.Rmd
Let me guide you through every word and every ride

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

@@

First download a friction surface — here using the motorised travel time from
Weiss *et al.* 2020.
```{r example}
library(traveltime)
library(terra)

@@

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = NA
)
```

@@

First download a friction surface — here using the motorised travel time from
Weiss *et al.* 2020.
```{r }
library(traveltime)
library(terra)

@@

## Let's go to Singapore

Here it is:
```{r}
library(sdmtools)
sin <- sdmtools::make_africa_mask(
  type = "vector",
  countries = "SGP"
)
plot(sin)
```
Get the extent of that `SpatVector` in the format we need it.
```{r}
sin_ext <- ext_from_spatraster(sin)
sin_ext
```

We're going to see how long it takes to walk home from Changi Airport. So we'll 
download the walking-only friction surface this time.
```{r }
library(traveltime)
library(terra)

friction_singapore <- get_friction_surface(
    surface = "walk2020",
    extent = sin_ext
  )|> 
  mask(sin)

friction_singapore
```

And where is Changi Airport?
```{r}
changi_airport <- tibble::tibble(
  x = c(103.984),
  y = c(1.355)
)
changi_airport
```
Let's look at those.
```{r}
plot(friction_singapore)
plot(sin, add = TRUE)
points(changi_airport, pch = 19, add = TRUE)
```

And calculate the travel time
```{r}
travel_time_sin <- calculate_travel_time(
  friction_surface = friction_singapore,
  points = changi_airport
)
travel_time_sin
```

Et voi*lah*!
```{r}
plot(travel_time_sin)
points(changi_airport, pch = 19, add = TRUE)
plot(sin, add = TRUE)
```
